MATD02 - Exploration of Finite Geometry

### 2024-11-12 paper/main.tex
Add some definition references for finite projective geometry

% Packages for formatting and math
\usepackage{amsmath, amsthm, amssymb}
\usepackage{cite}
\usepackage{geometry}
\geometry{a4paper, margin=2.5cm}

% Theorem and Proof setup
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

    \section{Synthetic geometry and higher dimensions}

    Notice we didn't have to talk about our points as being two-dimensional,
    however something about the axioms we used let us represent our spaces as two dimensional planes.

    Synthetic geometry studies such axiomatically defined geometries, and gives us tools to talk about
    higher dimensional spaces with set theoretic definitions of dimension.

    DEFINE projective plane axiomatically

    DEFINE geometric dimension

    \subsection{Projective spaces and geometric dimension}

    Projective planes are two-dimensional projective spaces

    \begin{theorem}
    \end{theorem}

@@

    \subsection{Finite projective planes of order $\geq 3$ }

@@

    Take a look at notes from the group theory textbooks.

>>>>

% Packages for formatting and math
\usepackage{amsmath, amsthm, amssymb}
\usepackage{cite}
\usepackage{geometry}
\usepackage{csquotes}
\geometry{a4paper, margin=2.5cm}

%\setlength{\parskip}{\baselineskip}%
%\setlength{\parindent}{0pt}
\usepackage{parskip}
\setlength{\parindent}{0pt}

% Theorem and Proof setup
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}

@@

    \section{Finite geometries in higher dimensions}

%    Synthetic geometry studies such axiomatically defined geometries, and gives us tools to talk about
%    higher dimensional spaces with set theoretic definitions of dimension.

    Notice we didn't have to talk about our points as being two-dimensional,
    however something about our choice of points let us represent our spaces as two-dimensional planes.

    In fact, when looking at projective geometry through the lens of infinite sets like $R$,
    we get a definition of \enquote{projective spaces} by looking at one-dimensional vector subspaces of a vector space like $R^n$.\cite{weisstein_projective_nodate}
%    The projective part of projective geometry can be thought of as adding points at infinity to such a vector space,
    Here, our dimension comes from a concept of coordinates in the underlying vector space.

    In the finite case however\textemdash especially working purely from axioms\textemdash we don't have such an obvious idea of dimension.
    We can, however, generalize concepts from vector spaces to get the following definitions.\cite{noauthor_projective_2024,beutelspacher_projective_2000}

%    A subspace of the projective space is a subset X, such that any line containing two points of X is a subset of X (that is, completely contained in X). The full space and the empty space are always subspaces.
    \begin{definition}
        A subspace of the projective space is a subset X, such that any line containing two points of X is a subset of X (that is, completely contained in X). The full space and the empty space are always subspaces.
    \end{definition}

    \begin{definition}
        The geometric dimension of the space $P$ is said to be n if that is the largest number for which there is a strictly ascending chain of subspaces of this form:
        \[\emptyset = X_{-1}\subset X_{0}\subset \cdots X_{n}=P.\]
    \end{definition}

    \begin{theorem}
        Projective planes are projective spaces of dimension 2.
    \end{theorem}

@@

    \subsection{Finite projective spaces of dimension $\geq 3$ }

@@
